Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-06-06 main.tex
:balloon: Update pbs scripts
:pencil: Update manuscript [in progress]

\begin{abstract}
	Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	We uniquely introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data, and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a fundamental scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
	Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
	A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
	Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
\end{abstract}

@@

	\begin{subsection}{Channel Reconfiguration}
		2
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

>>>>

\begin{abstract}
	Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	% We uniquely introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data, and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
	% We uniquely introduce the concept of Metascatter, which adjusts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data, and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
	% We uniquely introduce the concept of Metascatter, which adjusts the input distribution of a finite-state backscatter device based on \gls{csi}, to \emph{simultaneously} encode its own data and assist ambient transmission.
	% We uniquely introduce the concept of Metascatter, which \emph{simultaneously} encodes own message and assists ambient transmission, using adaptive input probability distribution based on \gls{csi}.
	We uniquely introduce the concept of Metascatter, which adapts the input distribution of a finite-state backscatter device based on \gls{csi}, to \emph{simultaneously} encode self message and assist ambient transmission.
	% Compared to existing strategies as modulation on IRS pattern
	Compared to conventional \gls{irs}-empowered \gls{sr} that considers encoding and beamforming independently (overlay or parallel), Metascatter revisits backscatter principles and bridges parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.

	% It enables smoother primary-backscatter tradeoff

	integrates \gls{irs} and \gls{sr} from backscatter principles

	% treat backscatter modulation and passive beamforming independently (overlay or distinction), Metascatter

	\gls{irs}-empowered \gls{sr} strategies that embed

	by adaptive input distribution design based on \gls{csi}.

	adjusts the input distribution of a finite-state backscatter device based on \gls{csi}, to \emph{simultaneously} encode its own data and assist ambient transmission.

	% It not only generalizes SR and IRS

	Compared to existing \gls{irs}-empowered \gls{sr},

	A flexible input distribution design

	Based on Channel State Information (CSI), the input distribution can be

	KKT tag input probability distribution for maximizing weighted sum of primary and total backscatter rate

	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a fundamental scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
	Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
	A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
	Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
\end{abstract}

@@

	\begin{subsection}{Channel Reconfiguration}
		2
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
	% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others
